MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
add notes for point Shot Clock Presure by Alex
I just started on this topic
I'll analyse this topic
win lose analysis

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage  
h. Fatigue Effect (Number of Rest Day)  
i.

@@

##Installing packages
```{r}
install.packages('reshape')

@@

```{r}
#adding columns for names of 'home' and 'away' teams
df[,"MATCHUP"] <- as.character(df[,"MATCHUP"])

for (i in 1:nrow(df)) {
  df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
}
```

```{r}
#combining columns for the analysis
library(reshape)
```

>>>>

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

@@

##Installing packages and calling libraries
```{r}
install.packages('reshape')
library(reshape)
library(ggplot2)

@@

```{r}
#adding columns for names of 'home' and 'away' teams. In addition, WINNER column tells which team won
df[,"MATCHUP"] <- as.character(df[,"MATCHUP"])
df[,"W"] <- as.character(df[,"W"])

for (i in 1:nrow(df)) {
  if (LOCATION[i]=="H") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
  if (W[i]=="W") df$WINNER[i] <- "HOME" 
  if (W[i]=="L") df$WINNER[i] <- "AWAY"}
  if (LOCATION[i]=="A") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7] 
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  if (W[i]=="L") df$WINNER[i] <- "HOME"  
  if (W[i]=="W") df$WINNER[i] <- "AWAY"}}

df$BLANK<-"" #for some reason cast function does not work with last column in dataframe, so I have created this BLANK column as I need to use AWAY_TEAM colum (it was a last column). 
```

```{r}
aa<- cast(df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + WINNER ~ W)

table(aa$WINNER) [2]
#home wins:
hh<-sum(aa$WINNER=="HOME")
#Away wins:
aw<-sum(aa$WINNER=="AWAY")
#percentage of home team winning: 
round(hh/(hh+aw),2)
```

```{r}
head(aa)
aa1<- cast(aa, HOME_TEAM  ~ WINNER); names(aa1)[1]<-"TEAM"
aa1$WIN_PCT_HOME<-round(aa1$HOME/(aa1$HOME+aa1$AWAY),2)

aa2<- cast(aa, AWAY_TEAM ~ WINNER); names(aa2)[1]<-"TEAM"
aa2$WIN_PCT_AWAY<-round(aa2$HOME/(aa2$HOME+aa2$AWAY),2)

aa3<- merge (aa1,aa2, by ="TEAM")
for (i in 1:nrow(aa3)) {if(aa3$WIN_PCT_HOME[i]>aa3$WIN_PCT_AWAY[i]) aa3$HOME_ADV[i]<-"YES" else aa3$HOME_ADV[i]<-"NO"}
head(aa3)

ggplot(aa3,aes(x=TEAM, y= WIN_PCT_HOME, col= HOME_ADV))+ geom_point()
#TO BE UPDATED
```
